### 2020-03-25 tex/confirm-service-activity.tex
edit confirm service activity section

\section{Confirm Service Activity}

>>>>

\section{Confirm Service Activity}
In this section, we present potential solutions for the confirm service activity 
problem. The goal is to come up with provably secure solutions that allows an 
Ursula to prove that it has served a given number of distinct re-encryption 
requests within a given period.

The rest of this section outlines the network and threat models adopted by 
the proposed solutions, provides an overview of the underlying cryptographic primitives and 
protocols, after which it discusses the proposed solutions along with an analysis of 
their security and efficiency aspects. Lastly, the section concludes with directions of 
future work on the confirm service activity issue.

### 2020-03-25 tex/confirm-service-activity/solutions.tex
edit confirm service activity section

\david{I think it is possible to aggregate current Umbral proofs. I started to explore this option in the past but there was no use for it at that moment.}

@@

At a high level, the scheme works as follows. For each round, a working Ursula keeps 
a full record of all the requests that she served during the round. These 
include the signed requests received from Bob(s), and the produced $cFrag$ 
and the correctness proof $\pi$ (as in the Umbral scheme) for 
each request. At the end of the round, a committee of $t$ Ursulas is 
elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
initiates the CoSi protocol to sign the message $m$ stated above while 
replacing $\omega$ with the actual number of served 
requests in the round. This Ursula sends $m$ along with the full report to 
each member in the committee. Each member Ursula (i.e., member in the 
elected committee) verifies $m$ by checking the report as follows:
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item Check that each request is distinct and valid by verifying Bob's 
signature over the request. (Here the policy will contain Bob's public 
key to allow the committee use the right verification key.)

\derek{Signature only validates request, but for distinct requests, presumably blockhash/sequence number needs to also be checked?}

>>>>

@@

At a high level, the scheme works as follows. For each round, a working Ursula keeps 
a full record of all the requests that she served during the round. These 
include the signed requests received from Bob(s), and the produced $cFrag$ 
and the correctness proof $\pi$ (as in the Umbral scheme) for 
each request. At the end of the round, a committee of $t$ Ursulas is 
elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
initiates the CoSi protocol to sign the message $m$ stated above while 
replacing $\omega$ with the actual number of served 
requests in the round. This Ursula sends $m$ along with the full report to 
each member in the committee. Each member Ursula (i.e., member in the 
elected committee) verifies $m$ by checking the report as follows:
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item Check that each request is distinct by checking the sequence 
number of the request (or any value that is used for freshaness), and valid by verifying Bob's 
signature over the request. (Here the policy will contain Bob's public 
key to allow the committee use the right verification key.)

### 2020-03-25 tex/confirm-service-activity/threat-network-model.tex
edit confirm service activity section

\subsubsection{Network Model}
In order for the proposed solutions to work, we need to ensure freshness, 
integrity, and authenticity of the requests issued by Bob. This can be achieved 
by requiring Bob to sign each request it issues and to include a timestamp, or 
sequence number, in each request to ensure freshness.

\david{NuCrypher currently supports this by allowing Bob to include a blockhash,
although it's not being used for the moment.}

The following approach can be used here; given that Umbral already requires Bob to 
have a key pair, this pair can be used for signing and verifying the signed requests. 
This also means that Ursula should be aware that the secret key can be used for
signing the requests and the public 
key should be known to Ursula to verify the signatures.

\david{Reusing the same keypair for encryption and signing may introduce some key management problems. Is it possible to find a solution that supports separate keypairs?}

\subsubsection{Threat Model}
We do not place trust in any party and we assume that all participants are 
self-interested. This means that a party may 
follow the protocol or deviate from it, either on its own or by colluding 
with other attackers, and decisions are solely based on what maximizes the financial profits
of this party. As such, Ursula may collude with Bob or Alice (by spinning 
its own Alice and/or Bob for example) to achieve her financial goals.

>>>>

\subsubsection{Network Model}
In order for the proposed solutions to work, we need to ensure freshness, 
integrity, and authenticity of the requests issued by Bob. This can be achieved 
by requiring Bob to sign each request it issues and to include a timestamp, or 
sequence number, in each request to ensure freshness. The keypair used for the 
signature should be separate from the keypair Bob uses for proxy encryption in the 
system.

Until now we assume that Alice pays for the service by using the Ether she locks 
in the policy contract. Other arrangement may emerge in the system like having 
Bob pay for each requests he issues. Such arrangement and its implication on the 
confirm service activity issue will be studied once it becomes part of the NuCypher 
network protocol.

\subsubsection{Threat Model}
We do not place trust in any party and we assume that all participants are 
self-interested. This means that a party may 
follow the protocol or deviate from it, either on its own or by colluding 
with other attackers, and decisions are solely based on what maximizes the financial profits
of this party. Thus, Ursula may collude with Bob or Alice (by spinning 
its own Alice and/or Bob for example) to achieve her financial goals. 
The latter is assumed in the current proposed solutions (PCD, CoSi, and 
challenge/open based schemes). This means that solutions provide higher 
security guarantees. It could be the case that relaxing the requirement of 
accounting for Bob/Ursula collusion allows deploying more efficient solutions. 
In order to make an educated decision of the plausibility of this threat, we need 
more data about the system operation and the behavior of the participants 
once the inflation rewards disappears in the system. As such, we leave this 
issue until later when fees become the only source of rewards for Ursulas.
